timesliced_random_cell_selection

### 2018-10-30 src/timesliced_random_cell_selection.Rmd
random timesliced files given yymm columns

```{r}
library(dplyr)
bckrnd_folder <- "../output/bio/background/raw/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder
randbckoutput <- "../output/bio/background/rand/" #where the files are to be saved to
# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  test_sel <- read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  test_sel <- sample_n(test_sel, 10000) #where 10000 = number of rows to sample (large sample as per maxent)
  write.csv(test_sel, file = paste0(randbckoutput, bckrnd_list[i]), row.names = FALSE) #dont need to add .csv as it's already in the filename
}

@@

```{r}

>>>>

```{r}
library(dplyr)
bckrnd_folder <- "../output/bio/background/raw/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder
randbckoutput <- "../output/bio/background/rand/" #where the files are to be saved to
# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  sel <- read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  sel <- sample_n(test_sel, 10000) #where 10000 = number of rows to sample (large sample as per maxent)
  write.csv(sel, file = paste0(randbckoutput, bckrnd_list[i]), row.names = FALSE) #dont need to add .csv as it's already in the filename
}

@@

```{r}
rand_folder <- "../output/bio/background/rand/"      # path to folder that holds multiple .csv files
rand_list <- list.files(path = rand_folder, pattern="*.csv") # create list of all .csv files in folder
randbckoutput <- "../output/bio/background/rand/" #where the files are to be saved to
for(i in 1:length(rand_list)){
  randtemp <- read.csv(paste(rand_folder, rand_list[i], sep=''))
  randtemp$year <- substr(rand_list[i], 1, 4)
  randtemp$month <- substr(rand_list[i], 6, 7)
  write.csv(randtemp, file = paste0(randbckoutput, bckrnd_list[i]), row.names = FALSE) #dont need to add .csv as it's already in the filename
}
```
note that in the output temp file in R shows a . after the month if that month is a single digit. The .csv outputs don't

ok now you can start to populate the rest of the background point information. The background points file should mirror as much as possible the occurence file
